\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{lipsum}                     % Dummytext
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{float}
\usepackage{tikz-qtree}
\usepackage{tikz}
\usepackage[linguistics]{forest}

\usepackage{amssymb}
\usepackage{amsmath}
\newcommand*{\QEDA}{\hfill\ensuremath{\blacksquare}}% filled box
\newcommand*{\QEDB}{\hfill\ensuremath{\square}}% unfilled box

% dem nice tables
\usepackage[hmargin=2cm,top=4cm,headheight=65pt,footskip=65pt]{geometry}
\usepackage{fmtcount} % for \ordinalnum
\usepackage{array,multirow}
\usepackage{tabularx}
\usepackage{lastpage}


% add a special collumn type
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}


%header/footer stuff
\usepackage{fancyhdr}
\pagestyle{fancy}

%note that if you do not do these blank ones, the package defaults to something
%you may not want in your header or footer
\lhead{Review for HHTAP}
\chead{}
\rhead{\today}
\lfoot{Isaak Cherdak}
\cfoot{}
\rfoot{\thepage}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\usepackage[english]{babel}
\emergencystretch=1pt
\usepackage[justification=centering]{caption}
\graphicspath{{Pictures/} }

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}

\usepackage{setspace}
\doublespacing

\title{Review for HHTAP}
\author{Isaak Cherdak}
%\date{} %blank date

\begin{document}

\maketitle

\tableofcontents

\pagebreak

\section{How does the author's approach or solution improve on previous
approaches to the problem that they are solving?}

Many current systems rely on global shared memory, system-wide cache coherence,
and massive parallel performance. However, this paper identifies that the new
hardware designs made by industry giants, particularly GPGPU improvements,
require an investigation into new DBMS engine designs. This paper provides an
architecture that is shown to be a step in this direction: Heterogenous Hybrid
Transactional and Analytical Processing (H$^2$TAP).

\section{Why is this work important?}

This paper describes a major turning point in technological advancement that
should warn DBMS engineers to start looking into new designs. Furthermore, it
shows its own system, H$^2$TAP and demonstrates that such modern designs are
important for modern DBMS engines.

\section{Provide 3+ comments/questions}

\begin{itemize}
  \item Why don't more companies use GPGPUs as major components of DBMS system
    hardware?
  \item Figure 5 is a good reference for getting an idea of the trade-off
    between maintaining lower transaction data percentages in hardware and the
    cost of additional hardware.
  \item This paper does a good job of providing information efficiently. A lot
    of new information was presented for a 11 page paper.
\end{itemize}

\end{document}
