\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{lipsum}                     % Dummytext
\usepackage{hyperref}
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{float}
\usepackage{tikz-qtree}
\usepackage{tikz}
\usepackage[linguistics]{forest}

\usepackage{amssymb}
\usepackage{amsmath}
\newcommand*{\QEDA}{\hfill\ensuremath{\blacksquare}}% filled box
\newcommand*{\QEDB}{\hfill\ensuremath{\square}}% unfilled box

% dem nice tables
\usepackage[hmargin=2cm,top=4cm,headheight=65pt,footskip=65pt]{geometry}
\usepackage{fmtcount} % for \ordinalnum
\usepackage{array,multirow}
\usepackage{tabularx}
\usepackage{lastpage}


% add a special collumn type
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}


%header/footer stuff
\usepackage{fancyhdr}
\pagestyle{fancy}

%note that if you do not do these blank ones, the package defaults to something
%you may not want in your header or footer
\lhead{Review for RocksDB}
\chead{}
\rhead{\today}
\lfoot{Isaak Cherdak}
\cfoot{}
\rfoot{\thepage}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\usepackage[english]{babel}
\emergencystretch=1pt
\usepackage[justification=centering]{caption}
\graphicspath{{Pictures/} }

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}

\usepackage{setspace}
\doublespacing

\title{Review for RocksDB}
\author{Isaak Cherdak}
%\date{} %blank date

\begin{document}

\maketitle

\section{How does the author's approach or solution improve on previous
approaches to the problem that they are solving?}

RocksDB is more concerned with space optimization than throughput and latency.
More specifically, once throughput and latency achieve acceptable levels the
primary focus becomes on space utilization. This is especially important for
Facebook which has to handle data for millions of users of their website.

\section{Why is this work important?}

RocksDB really brought the LSM tree to light in ways that were not done before.
The primary difference that RocksDB mentions about the usefulness of the LSM
tree is on space optimization and decreased write amplification rather than the
previously known benefit of minimized random writes to storage. It's not so much
that the latter is no longer true, but rather that the former was found to be a
much more useful benefit through the development of RocksDB.

\section{Provide 3+ comments/questions}

\begin{itemize}
  \item It's intersting that even though the focus is on space optimization,
    RocksDB performs better in throughput and latency in some ways than other
    database systems whose concerns with latency and throughput are more
    primary. Even so, RocksDB used about 50\% of the storage space that InnoDB
    needed for the same data.
  \item The first graph for 1B Vertices/50GB DRAM seems to have strange numbers
    compared to that of the graph to the left. How is it that having vertices 6
    orders of magnitude smaller would increase space utilization by an order of
    magnitude?
  \item The paper discusses the use of Bloom Filters in a very hand-wavy
    approach: switching from saying that it saves time on average case to a
    discussion about prefix filters or space utilization/performance tradeoffs
    of lowest level bloom filters. Particularly in the discussion of space
    tradeoffs for the last level bloom filter: isn't this more a concern of the
    ratio of last level bloom filter space to total amount of available space?
\end{itemize}

\end{document}
